\begin{itemize}
\item Cramer's rule
$$
\begin{aligned}ax+by=e\\cx+dy=f\end{aligned}
\Rightarrow
\begin{aligned}x=\dfrac{ed-bf}{ad-bc}\\y=\dfrac{af-ec}{ad-bc}\end{aligned}
$$

\item Vandermonde's Identity
$$
C(n + m, k) = \sum_{i=0}^k C(n, i)C(m, k - i)
$$

\item Burnside's Lemma

Let us calculate the number of necklaces of $n$ pearls, where each pearl has $m$ possible colors. Two necklaces are symmetric if they are similar after rotating them. There are $n$ ways to change the position of a necklace, because we can rotate it $0, 1, \dots, n_1$ steps clockwise. If the number of steps is 0, all $m^n$ necklaces remain the same, and if the number of steps is $1$, only the $m$ necklaces where each pearl has the same color remain the same. More generally, when the number of steps is $k$, a total of $m^\gcd(k,n)$ necklaces remain the same. The reason for this is that blocks of pearls of size $\gcd(k, n)$ will replace each other. Thus, according to Burnside’s lemma, the number of necklaces is $\sum_{i = 0}^{n - 1} \frac{m^\gcd(i, n)}{n}$. For example, the number of necklaces of length $4$ with $3$ colors is $\frac{3^4 + 3 + 3^2 + 3}{4} = 24$

\item Lindström–Gessel–Viennot Lemma

## 定義

$\omega(P)$ 表示 $P$ 這條路徑上所有邊的邊權之積。 （路徑計數時，可以將邊權都設為 $1$）（事實上，邊權可以為生成函數）
$e(u, v)$ 表示 $u$ 到 $v$ 的 **每一條** 路徑 $P$ 的 $\omega(P)$ 之和，即 $e(u, v)=\sum\limits_{P:u\rightarrow v}\omega(P)$。
起點集合 $A$，是有向無環圖點集的一個子集，大小為 $n$。終點集合 $B$，也是有向無環圖點集的一個子集，大小也為 $n$。
一組 $A\rightarrow B$ 的不相交路徑 $S$：$S_i$ 是一條從 $A_i$ 到 $B_{\sigma(S)_i}$ 的路徑（$\sigma(S)$ 是一個排列），對於任何 $i\ne j$，$S_i$ 和 $S_j$ 沒有公共頂點。
$t(\sigma)$ 表示排列 $\sigma$ 的逆序對個數。

$$
M = \begin{bmatrix}e(A_1,B_1)&e(A_1,B_2)&\cdots&e(A_1,B_n)\\
e(A_2,B_1)&e(A_2,B_2)&\cdots&e(A_2,B_n)\\
\vdots&\vdots&\ddots&\vdots\\
e(A_n,B_1)&e(A_n,B_2)&\cdots&e(A_n,B_n)\end{bmatrix}
$$

$$
\det(M)=\sum\limits_{S:A\rightarrow B}(-1)^{t(\sigma(S))}\prod\limits_{i=1}^n \omega(S_i)
$$

其中 $\sum\limits_{S:A\rightarrow B}$ 表示滿足上文要求的 $A\rightarrow B$ 的每一組不相交路徑 $S$。

\item Kirchhoff's Theorem

Denote $L$ be a $n \times n$ matrix as the Laplacian matrix of graph $G$, where $L_{ii} = d(i)$, $L_{ij} = -c$ where $c$ is the number of edge $(i, j)$ in $G$.
\begin{itemize}
    \itemsep-0.5em
    \item The number of undirected spanning in $G$ is $\lvert \det(\tilde{L}_{11}) \rvert$.
    \item The number of directed spanning tree rooted at $r$ in $G$ is $\lvert \det(\tilde{L}_{rr}) \rvert$.
\end{itemize}

\item Tutte's Matrix

Let $D$ be a $n \times n$ matrix, where $d_{ij} = x_{ij}$ ($x_{ij}$ is chosen uniformly at random) if $i < j$ and $(i, j) \in E$, otherwise $d_{ij} = -d_{ji}$. $\frac{rank(D)}{2}$ is the maximum matching on $G$.

\item Cayley's Formula

\begin{itemize}
    \itemsep-0.5em
  \item Given a degree sequence $d_1, d_2, \ldots, d_n$ for each \textit{labeled} vertices, there are $\frac{(n - 2)!}{(d_1 - 1)!(d_2 - 1)!\cdots(d_n - 1)!}$ spanning trees.
  \item Let $T_{n, k}$ be the number of \textit{labeled} forests on $n$ vertices with $k$ components, such that vertex $1, 2, \ldots, k$ belong to different components. Then $T_{n, k} = kn^{n - k - 1}$.
\end{itemize}

\item Erdős–Gallai theorem 

A sequence of nonnegative integers $d_1\ge\cdots\ge d_n$ can be represented as the degree sequence of a finite simple graph on $n$ vertices if and only if $d_1+\cdots+d_n$ is even and $\displaystyle\sum_{i-1}^kd_i\le k(k-1)+\displaystyle\sum_{i=k+1}^n\min(d_i,k)$ holds for every $1\le k\le n$.

\item Gale–Ryser theorem

A pair of sequences of nonnegative integers $a_1\ge\cdots\ge a_n$ and $b_1,\ldots,b_n$ is bigraphic if and only if $\displaystyle\sum_{i=1}^n a_i=\displaystyle\sum_{i=1}^n b_i$ and $\displaystyle\sum_{i=1}^k a_i\le \displaystyle\sum_{i=1}^n\min(b_i,k)$ holds for every $1\le k\le n$.

\item Fulkerson–Chen–Anstee theorem

A sequence $(a_1,b_1),\ldots,(a_n,b_n)$ of nonnegative integer pairs with $a_1\ge\cdots\ge a_n$ is digraphic if and only if $\displaystyle\sum_{i=1}^n a_i=\displaystyle\sum_{i=1}^n b_i$ and $\displaystyle\sum_{i=1}^k a_i\le \displaystyle\sum_{i=1}^k\min(b_i,k-1)+\displaystyle\sum_{i=k+1}^n\min(b_i,k)$ holds for every $1\le k\le n$.

\item Möbius inversion formula

\begin{itemize}
    \itemsep-0.5em
  \item $f(n)=\sum_{d\mid n}g(d)\Leftrightarrow g(n)=\sum_{d\mid n}\mu(d)f(\frac{n}{d})$
  \item $f(n)=\sum_{n\mid d}g(d)\Leftrightarrow g(n)=\sum_{n\mid d}\mu(\frac{d}{n})f(d)$
\end{itemize}

\item Spherical cap

\begin{itemize}
    \itemsep-0.5em
  \item A portion of a sphere cut off by a plane.
  \item $r$: sphere radius, $a$: radius of the base of the cap, $h$: height of the cap, $\theta$: $\arcsin(a/r)$.
  \item Volume $=\pi h^2(3r-h)/3=\pi h(3a^2+h^2)/6=\pi r^3(2+\cos\theta)(1-\cos\theta)^2/3$.
  \item Area $=2\pi rh=\pi(a^2+h^2)=2\pi r^2(1-\cos\theta)$.
\end{itemize}

\end{itemize}
